---
title: "SCGIS Vancouver"
title-block-banner: "img/home/yvr_dsm.png"
format:
  html:
    css: styles.css
---

::::: {.column-screen .blue-section style="background-color:#253351;"}
:::: {.column-screen-inset}
::: {style="max-width: 650px; margin: 0 auto; color:white; padding:1.5rem 0; text-align:center;"}
Welcome to the homepage for the newly formed (*est.* November 2025) **Vancouver, BC Chapter of the Society for Conservation GIS**.

Our chapter is an affiliated chapter of the <a href="https://www.scgis.org/" style="color:#cce8ff; text-decoration:underline;">Society for Conservation GIS (SCGIS)</a>. SCGIS helps bring together conservation practitioners and GIS technology by supporting communication and networking, scholarships, and training across the world through a system of connected <a href="https://www.scgis.org/chapters" style="color:#cce8ff; text-decoration:underline;">chapters</a> in various cities and countries. Membership is open to anyone looking to engage in the GIS conservation community.
:::
::::
:::::

::::: {.column-screen style="background-color:#ffffff;"}
:::: {.column-screen-inset}
::: {.home-column-image .col-left}
<a href="about.html"></a>
:::

::: {.home-column-text .col-right}
<center>

<h1 class="heading-home" style="color: #152F55;">

About Us

</h1>

::: {style="max-width: 650px; margin: 0 auto;"}
<p style="color:#152F55; font-style: italic;">

This group aims to bring together the community of conservation-related Geographic Information System (GIS) practitioners across Vancouver and the broader region of southern British Columbia. Membership to our Chapter is free and open to anyone! Check out our **Members Map** below (anonymous), or learn more on our [About Us](about.html) page. You can sign up to be a member by joining our [Mailing List](mailing_list.html) (Below).

</p>
:::



::: {style="max-width: 650px; margin: 0 auto;padding:1.5rem 0"}
```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(leaflet); library(terra)



members <- read.csv("https://raw.githubusercontent.com/scgis-canada-vancouver/scgis-canada-vancouver.github.io/main/Member_map.csv")



members.vect <- vect(members, geom = c("lng", "lat"), crs = "EPSG:4326")


leaflet(members.vect) %>%
  addProviderTiles("Esri.WorldImagery") %>%
  addMarkers(
    clusterOptions = markerClusterOptions(
      singleMarkerMode = TRUE
    )
  ) %>%
  addMiniMap(
    tiles = providers$Esri.WorldImagery,  # same tile provider as main map
    toggleDisplay = TRUE,                 # show a collapse/expand button
    aimingRectOptions = list(
      color = "#FFF",   # outline color
      weight = 2,          # line thickness
      opacity = 1,         # full opacity
      fillColor = "#FFF",  # fill color
      fillOpacity = 0       # transparency of fill
    ),
    minimized = FALSE,                    # start expanded
    zoomLevelOffset = -6     
  )%>%
   # --- Load the EdgeMarker plugin JS into this widget ---
  htmlwidgets::prependContent(
    htmltools::tags$script(
      src = "https://cdn.jsdelivr.net/gh/ubergesundheit/Leaflet.EdgeMarker/Leaflet.EdgeMarker.js"
    )
  ) %>%
  # --- Add watermark AND edge markers in a single onRender() ---
  htmlwidgets::onRender("
    function(el, x) {
      // --- Watermark control ---
      L.Control.Watermark = L.Control.extend({
        onAdd: function(map) {
          var img = L.DomUtil.create('img');
          img.src = 'img/home/scgis_logo.png';   // adjust path as needed
          img.style.width = '100px';
          return img;
        },
        onRemove: function(map) {
          // nothing to do
        }
      });

      L.control.watermark = function(opts) {
        return new L.Control.Watermark(opts);
      };

      L.control.watermark({ position: 'bottomleft' }).addTo(this);

      // --- EdgeMarker plugin ---
      if (L.edgeMarker) {
        var edgeMarkerLayer = L.edgeMarker({
          icon: L.icon({
            iconUrl: 'img/home/arrow.png',
            clickable: true,
            iconSize: [48, 48],
            iconAnchor: [24, 24]
          }),
          rotateIcons: true,
          layerGroup: null // null = look at all markers / circles on the map
        }).addTo(this);
      } else {
        console.error('Leaflet.EdgeMarker plugin was not loaded correctly.');
      }
    }
  ") %>%
  setView(-123.1007, 49.2527, 11)



```

:::



::::: {.column-screen .full-bleed-blue style="background-color:#253351;"}
:::: {.column-screen-inset}
::: {.home-column-image .col-left}
<a href="events.html#upcoming-events"></a>
:::

::: {.home-column-text .col-right}
<center>

<h1 class="heading-home" style="color: #ffffff;">
Events
</h1>

::: {style="max-width: 650px; margin: 0 auto;"}
<p style="color:#ffffff; font-style: italic;">
SCGIS Vancouver hosts a variety of events, including talks from conservation and GIS specialists and groups, hands-on workshops, outdoor citizen science, and social mixers. Check out past and upcoming events here! Be sure to sign up for our mailing list (above) and follow us on social media for updates.
</p>
:::

```{r, echo = FALSE}
#| warning: false

library(htmltools)

tags$div(class = "category-row",

  # --- PAST EVENTS (left) ---
  tags$div(
    class = "category-column",
    tags$a(
      href = "past_events.html",
      tags$img(
        src = "images/vectors/history_white.svg",
        class = "category-image"
      )
    ),
    tags$h4(
      style = "text-align:center;",
      tags$a(
        class = "category-link-white",
        href = "past_events.html",
        "Past Events"
      )
    )
  ),

  # --- UPCOMING EVENTS (middle) ---
  tags$div(
    class = "category-column",
    tags$a(
      href = "upcoming_events.html",
      tags$img(
        src = "images/vectors/event_white.svg",
        class = "category-image"
      )
    ),
    tags$h4(
      style = "text-align:center;",
      tags$a(
        class = "category-link-white",
        href = "upcoming_events.html",
        "Upcoming Events"
      )
    )
  ),
  
  # --- Mailing List (right) ---
  tags$div(
    class = "category-column",
    tags$a(
      href = "mailing_list.html",
      tags$img(
        src = "images/vectors/mail_list_white.svg",
        class = "category-image"
      )
    ),
    tags$h4(
      style = "text-align:center;",
      tags$a(
        class = "category-link-white",
        href = "mailing_list.html",
        "Mailing List"
      )
    )
  )
)
```


<br>

</center>
:::
:::: 
:::::

::::: {.column-screen style="background-color:#ffffff;"}
:::: {.column-screen-inset}
::: {.home-column-image .col-left}
<a href="https://scgisvancouver.org/resources.html"></a>
:::

::: {.home-column-text .col-right}

<center> <h1 class="heading-home" style="color: #152F55;"> Resources </h1>

[Curated data portals, hubs, and papers related to conservation GIS in Vancouver, BC]{style="color: #152F55; font-style: italic"}

</center>

```{r, echo = FALSE}
#| warning: false

library(htmltools)

tags$div(class = "category-row",
         
  tags$div( 
    class = "category-column",
    tags$a(href = "data_portals.html",
      tags$img(
        href = "data_portals.html",
        src = "images/vectors/data_blue.svg",
        class = "category-image-blue"

  )),
  tags$h4(style = "text-align:center;",
      tags$a(
        class = "category-link-blue",
        href = "https://scgisvancouver.org/data_portals.html", "Data Portals"))),
  
  tags$div( 
    class = "category-column",
    tags$a(href = "cons_env_hubs.html",
      tags$img(
        href = "cons_env_hubs.html",
        src = "images/vectors/hub_blue.svg",
        class = "category-image-blue"
  )),
  tags$h4(style = "text-align:center",
      tags$a(
        class = "category-link-blue",
        href = "https://scgisvancouver.org/cons_env_hubs.html", "Conservation Hubs"))),
  
  tags$div( 
    class = "category-column",
    tags$a(href = "publications_news.html",
      tags$img(
        href = "publications_news.html",
        src = "images/vectors/publication_blue.svg",
        class = "category-image-blue"
  )),
  tags$h4(style = "text-align:center",
      tags$a(
        class = "category-link-blue",
        href = "https://scgisvancouver.org/publications_news.html", "Publications & News")))
  
  
  
  )
```

</center> 

:::


