---
title: "SCGIS Vancouver"
title-block-banner: "img/home/yvr_dsm.png"
format:
  html:
    css: styles.css
---

::: column-margin
```{=html}
<div class="card" style="padding:1rem; border-radius:10px;">
  <h5 class="card-title" style="margin:0;">Mailing List</h5>
  <p class="card-subtitle mb-3" style="margin:.25rem 0 1rem 0; opacity:.8;">
    Join the mailing list for event updates.
  </p>

  <form id="signup-form">
    <label for="email" style="display:block; margin-top:.6rem; font-weight:600;">Email</label>
    <input id="email" name="email" type="email" required autocomplete="email"
           style="width:100%; padding:.5rem; border:1px solid #ccc; border-radius:8px;">

    <label for="firstName" style="display:block; margin-top:.6rem; font-weight:600;">First Name</label>
    <input id="firstName" name="firstName" type="text" required autocomplete="given-name"
           style="width:100%; padding:.5rem; border:1px solid #ccc; border-radius:8px;">

    <label for="lastName" style="display:block; margin-top:.6rem; font-weight:600;">Last Name</label>
    <input id="lastName" name="lastName" type="text" required autocomplete="family-name"
           style="width:100%; padding:.5rem; border:1px solid #ccc; border-radius:8px;">

    <label for="affiliation" style="display:block; margin-top:.6rem; font-weight:600;">Affiliation</label>
    <input id="affiliation" name="affiliation" type="text" autocomplete="organization"
           style="width:100%; padding:.5rem; border:1px solid #ccc; border-radius:8px;">

    <button type="submit"
            style="margin-top:1rem; padding:.6rem 1rem; border:0; border-radius:8px; cursor:pointer;background-color: #277d8e; color: white;">
      Sign Up
    </button>
  </form>

  <div id="signup-msg" aria-live="polite" style="margin-top:.6rem; font-size:.95rem;"></div>
</div>

<script>
  // Your deployed Apps Script Web App URL (must be the /exec URL)
  const WEB_APP_URL =
    "https://script.google.com/macros/s/AKfycbz_JkgiIFZNZlUv1OHENZJJvqQbEyRB3azFXZNKuaKwuYc_tNAPGgmDpPmsRhLLDBE/exec";

  const form = document.getElementById("signup-form");
  const msg  = document.getElementById("signup-msg");

  form.addEventListener("submit", async (e) => {
    e.preventDefault();
    msg.textContent = "Submitting…";

    const payload = {
      email:       document.getElementById("email").value.trim(),
      firstName:   document.getElementById("firstName").value.trim(),
      lastName:    document.getElementById("lastName").value.trim(),
      affiliation: document.getElementById("affiliation").value.trim()
    };

    try {
      await fetch(WEB_APP_URL, {
        method: "POST",
        mode: "no-cors",
        headers: { "Content-Type": "application/json" },
        body: JSON.stringify(payload)
      });
      form.reset();
      msg.textContent = "Thanks! You're on the list.";
    } catch (err) {
      console.error(err);
      msg.textContent = "Sorry—something went wrong. Please try again.";
    }
  });
</script>
```
:::




<div style="max-width: 800px; margin: 0 auto;"> <p> Welcome to the homepage for the newly formed (<em>est.</em> November 2025) <strong>Vancouver, BC Chapter of the Society for Conservation GIS</strong>. </p> <p> This group aims to bring together the community of conservation-related Geographic Information System (GIS) practitioners across Vancouver and the broader region of southern British Columbia. </p> <p> Our chapter is an affiliated chapter of the <a href="https://www.scgis.org/" title="SCGIS Organization Homepage" style="color:#cce8ff; text-decoration:underline;"> Society for Conservation GIS (SCGIS) </a>. </p> <p> SCGIS helps bring together conservation practitioners and GIS technology by supporting communication and networking, scholarships, and training across the world through a system of connected <a href="https://www.scgis.org/chapters" title="Check out other SCGIS chapters around the world!" style="color:#cce8ff; text-decoration:underline;"> chapters </a> in various cities and countries. Membership is open to anyone looking to engage in a GIS conservation community. </p> </div> <br> <br> <br> <br> <br>



<br>
<br>
<br>
<br>
<br>



:::::: {.column-screen style="background-color:#ffffff;"}
::::: column-screen-inset
::: {.home-column-image .col-left}
<a href="events.html#upcoming-events"></a>
:::

::: {.home-column-text .col-right}
<center>

<h1 class="heading-home" style="color: #152F55;">
Events
</h1>

<div style="max-width: 650px; margin: 0 auto;">
  <p style="color:#152F55; font-style: italic;">
    SCGIS Vancouver hosts a variety of events, including talks from conservation and GIS specialists and groups, hands-on workshops, outdoor citizen science, and social mixers. 
    Check out past and upcoming events here! Be sure to sign up for our mailing list (above) and follow us on social media for updates. 
  </p>
</div>

</center>

```{r, echo = FALSE}
#| warning: false

library(htmltools)


tags$div(class = "category-row",

  # --- PAST EVENTS (left) ---
  tags$div(
    class = "category-column",
    tags$a(
      href = "past_events.html",   # <--- past events tab
      tags$img(
        src = "images/vectors/history.svg",
        class = "category-image"
      )
    ),
    tags$h4(
      style = "text-align:center; color:#152F55;",
      tags$a(
        style = "color:#152F55; text-decoration:none;",
        href = "past_events.html",
        "Past Events"
      )
    )
  ),

  # --- UPCOMING EVENTS (right) ---
  tags$div(
    class = "category-column",
    tags$a(
      href = "upcoming_events.html",   # <--- upcoming events tab
      tags$img(
        src = "images/vectors/event.svg",
        class = "category-image"
      )
    ),
    tags$h4(
      style = "text-align:center; color:#152F55;",
      tags$a(
        style = "color:#152F55; text-decoration:none;",
        href = "upcoming_events.html",
        "Upcoming Events"
      )
    )
  )
)
```


:::::: {.column-screen style="background-color:#152F55;"}
::::: column-screen-inset
::: {.home-column-image .col-left}
<a href="https://scgisvancouver.org/resources.html">

</a>
:::

::: {.home-column-text .col-right}
<center>

<h1 class="heading-home" style="color: #fff;">

Resources

</h1>

[Curated data portals, hubs, and papers related to conservation in Vancouver, BC ]{style="color: #fff; font-style: italic"}

</center>

```{r, echo = FALSE}
#| warning: false

library(htmltools)

tags$div(class = "category-row",
         
  tags$div( 
    class = "category-column",
    tags$a(href = "resources.html#data-portals",
      tags$img(
        href = "resources.html#data-portals",
        src = "images/vectors/data.svg",
        style = "color:#fff !important;",
        class = "category-image honey-white"
  )),
  tags$h4(style = "text-align:center;",
      tags$a(
        class = "white",
        href = "https://scgisvancouver.org/resources.html#data-portals", "Data Portals"))),
  
  tags$div( 
    class = "category-column",
    tags$a(href = "resources.html#conservation-environmental-data-hubs",
      tags$img(
        href = "resources.html#conservation-environmental-data-hubs",
        src = "images/vectors/hub.svg",
        style = "color:#fff !important;",
        class = "category-image honey-white"
  )),
  tags$h4(style = "text-align:center",
      tags$a(
        class = "white",
        href = "https://scgisvancouver.org/resources.html#conservation-environmental-data-hubs", "Conservation Hubs"))),
  
  tags$div( 
    class = "category-column",
    tags$a(href = "resources.html#relevant-publications-news",
      tags$img(
        href = "resources.html#relevant-publications-news",
        src = "images/vectors/publications.svg",
        style = "color:#fff !important;",
        class = "category-image honey-white"
  )),
  tags$h4(style = "text-align:center",
      tags$a(
        class = "white",
        href = "https://scgisvancouver.org/resources.html#relevant-publications-news", "Publications & News")))
  
  
  
  )
```
:::
:::::
::::::
